Short and Mechanized Logical Relation for Dependent Type Theory

### 2024-02-24 paper/paper.tex
Typo

However, with a little more effort, it is possible to recover a
precise algorithm. The first step is to define a deterministic
small-step reduction relation that is normalizing; that is, the
relation can always find a normal form if there exists one. A good
candidate is the leftmost-outermost reduction strategy. Its
normalizing property is standard and can be proven using the
factorization technique discussed in
\citet{takahashi-parallel-reduction, factorization-essentially}. By
composing the existence of normal form and the fact that the
deterministic relation is normalizing, we can derive show the
accessibility of the deterministic reduction relation
(\mintedinline{coq}{Acc} in Coq), and use the accessibility proof as
an induction metric to define an executable algorithm.

>>>>

However, with a little more effort, it is possible to recover a
precise algorithm. The first step is to define a deterministic
small-step reduction relation that is normalizing; that is, the
relation can always find a normal form if there exists one. A good
candidate is the leftmost-outermost reduction strategy. Its
normalizing property is standard and can be proven using the
factorization technique discussed in
\citet{takahashi-parallel-reduction, factorization-essentially}. By
composing the existence of normal form and the fact that the
deterministic relation is normalizing, we can derive show the
accessibility of the deterministic reduction relation
(\mintinline{coq}{Acc} in Coq), and use the accessibility proof as
an induction metric to define an executable algorithm.
